---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
  html_document:
    self_contained: false
    toc: true
    toc_float: false
---

```{r rsetup,eval=TRUE,include=FALSE}
require(codecheck)
require(knitr)
require(rprojroot)
require(yaml)
require(xtable)
require(tibble)
require(readr)
options(width=60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r rsetup-knitr,eval=TRUE,include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")


## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}


  
## get_outputs = function(manifest) {
##   files = sapply(manifest, function(x) x$file)
##   comments = sapply(manifest, function(x) x$comment)
##   sizes = file.size(dest_files)
##   url=sprintf('<a href="%s">%s</a>', dest_files, files)
##   table = cbind(files, comments, sizes, url)
##   table
## }

manifest_df = copy_manifest_files(root, manifest,
                                  dest_dir, keep_full_path=FALSE)
                                    
```



---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r .url_it(metadata$report)`
---



```{r,echo=FALSE,results='asis'}
latex_summary_of_metadata(metadata)
```


```{r, echo=FALSE,results='asis'}
xt = xtable(manifest_df[, c("output", "comment", "size")],
            digits=0,
            caption="Summary of output files generated")
print(xt, include.rownames=FALSE, comment=FALSE)
```


# Summary

This code was straightforward to codecheck; no issues were found.



\clearpage

# CODECHECKER notes

The github repo <https://github.com/adamkucharski/2020-cov-tracing>
was cloned.  The code was written in R and contained everything.  A
new file `install.R` was created to install the necessary packages.

```{r, code = readLines("../install.R"), eval=FALSE,echo=TRUE}
```

The outputs were found in the `outputs` folder, so this was moved to
`outputs-safe` and the R script edited to create a new outputs folder.

The startup folder was changed to comment out the line:
```{r}
##setwd("~/Documents/GitHub/2020-cov-tracing/")
```

## Running the software to regenerate outputs.

The program was run from the root directory using:
```{bash, eval=FALSE}
R
R> source("scripts/contact_model.R")
```
This took almost 9 minutes to complete on a Thinkpad laptop.

I would have preferred to run the script using the following:
```{bash, eval=FALSE}
Rscript scripts/contact_model.R
```

but this didn't generate the output images as `dev.copy()` does not
work in batch mode.

\setcounter{table}{0}
\setcounter{figure}{0}
\captionsetup[table]{labelformat=addC}
\captionsetup[figure]{labelformat=addC}


\clearpage

```{r, echo=FALSE, fig.cap=manifest_df[1:7,"comment"]}
knitr::include_graphics(manifest_df[1, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[2, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[3, "dest"])
cat('\n\n')
knitr::include_graphics(manifest_df[4, "dest"])
cat('\n\n')
```

\clearpage
# About this document

This document was created using Rmarkdown.  `make codecheck.pdf` will
regenerate the file.

```{r}
sessionInfo()
```




<!-- 
  rmarkdown::render("hancock1992-codecheck.Rmd", output_format="pdf_document") 
  -->
